### 2022-07-03 manuscript/manuscript.Rmd
aesthetic changes to figures

[**Figure 1**]{#fig1}. Relationship between corrected age (in months) and developmental domains. Left panel: regression lines represent predicted values estimated from GAM models (red lines) and 100 bootstrap replicates (gray lines), points and error bars represent the mean and standard error at 5-month age intervals. Right panel: effect derivatives and their CI~95%~, representing how the effect of corrected age (in months) in developmental domains changes across corrected age. Significant areas consider CI~95%~ that do not cross zero.

>>>>

[**Figure 1**]{#fig1}. Relationship between corrected age (in months) and developmental domains. Left panel: regression lines represent predicted values estimated from GAM models (bold red lines) and 200 bootstrap replicates (faded red lines), points and error bars represent the mean and standard error at 5-month age intervals. Right panel: effect derivatives and their CI~95%~, representing how the effect of corrected age (in months) in developmental domains changes across corrected age. Significant areas consider CI~95%~ that do not cross zero.
